Effective collector efficiency of sparse and dense arrays of emergent cylindrical collectors in laminar-turbulent transitional flows

### 2020-08-18 drafts/outline.tex
Overleaf, mostly Candace

\begin{figure}[htbp]
\includegraphics[width=15cm]{flume.png}
\centering
\caption{Conceptual diagram of the laboratory flume. Labeled parts are: 1) pump, 2) magnetic flowmeter, 3) test section, and 4) honeycomb flow collimator. Arrows indicate direction of flow. A side view of the open-channel part of the system is included. Some dimensions not to scale.}
\label{fig:floorplan}
\end{figure}

@@

\begin{figure}[htbp]
\includegraphics[width=15cm] {wf5-200sizedist.png}
\centering
\caption{Particle size distribution of WF5-200 walnut shell flour used as sediment in experiments, expressed as a probability density function (left) and cumulative density function (right). The mode of the distribution (left) and the 50th and 84th percentiles (right) are labeled.} %TODO get rid of red X's and make a clean, high-res version of figure
\label{fig:sedsize}
\end{figure}

@@

\subsection{Turbulence and Bed Shear Stress}
%not sure what to call this subsection 
Measurements taken by the ADV were filtered and despiked. Points in the time series that had low autocorrelation and points where there were large discrepancies between the two velocity measurements in the $z$ direction were excluded from analysis. Furthermore, we utilized the threshold ADV despiking algorithm detailed in Goring and Nikora (2002) in order to detect spikes in the data, as well as replace these spikes using cubic interpolation.
%need to cite this

Turbulence kinetic energy (TKE) was then calculated from the cleaned data using the equation 
\[\frac{1}{2}(<u^{'2}> + <v^{'2}> + <w^{'2}>)\,,\]
in which, with respect to flow, $u$ denotes velocity in the longitudinal direction, $v$ in the transverse direction, and $w$ in the vertical direction. This calculation was done for each of the four heights we took measurements at in the flume, and for each Reynolds number and collector density in our parameter space. Because the velocimeter recorded three measurements simultaneously at each timepoint, TKE was calculated separately for these three measurements.

Velocity measurements were also used to estimate bed shear stress. Biron et al. (2004) describes three different methods of estimating bed shear stress from Reynolds stress, TKE, and a modified turbulence kinetic energy, in which only fluctuations in the vertical direction are taken into account.%TODO

>>>>

\begin{figure}[htbp]
\includegraphics[width=15cm]{pics/flume_with_sedtraps.png}
\centering
\caption{Conceptual diagram of the laboratory flume. Labeled parts are: 1) pump, 2) magnetic flowmeter, 3) test section, and 4) honeycomb flow collimator. Arrows indicate direction of flow. A side view of the open-channel part of the system is included. Some dimensions not to scale. The locations of the sediment traps are marked on the top view of the diagram with red circles and on the side view with black cylinders.}
\label{fig:floorplan}
\end{figure}

@@

\begin{figure}[htbp]
\includegraphics[width=15cm] {wf5-200sizedist.png}
\centering
\caption{Particle size distribution of WF5-200 walnut shell flour used as sediment in experiments, expressed as a probability density function (left) and cumulative density function (right). The mode of the distribution (left) and the 50th and 84th percentiles (right) are labeled.} 
\label{fig:sedsize}
\end{figure}

@@

\subsection{Settling and Capture}
The mass of sediment settled due to gravity was estimated by weighing oven-dried sediment trap microfiber filter papers before and after each experiment and scaling the mass of sediment by the area of the sediment trap. As there were no significant differences between sediment mass collected laterally and longitudinally with respect to flow throughout the test section, the mass settled per sediment trap area was then averaged across all nine traps. Settling outside of the test section was calculated using this process on sediment traps taken from only our control experiments in which no dowels were installed, and scaling the average mass settled per trap area by the area of the flume without the test section ($1.98\, m^{2}$). Settling inside the test section was calculated using the same process on sediment traps taken from each experiment with dowels, and scaling the average mass settled per trap area by the area of the test section ($1.17\, m^{2}$). Total mass of sediment settled throughout the flume is the sum of settling inside and outside the test section.
% i'm not sure if this should go here. help!! also something about rate of settling should probably be here

\subsection{Turbulence and Bed Shear Stress}
Measurements taken by the ADV were filtered and despiked. Points in the time series that had low autocorrelation and points where there were large discrepancies between the two velocity measurements in the $z$ direction were excluded from analysis. Furthermore, we utilized the threshold ADV despiking algorithm detailed in Goring and Nikora (2002) in order to detect spikes in the data, as well as replace these spikes using cubic interpolation.
%need to cite this

Turbulence kinetic energy (TKE) was then calculated from the cleaned data using the equation 
\[\frac{1}{2}(<u^{'2}> + <v^{'2}> + <w^{'2}>),\]
in which, with respect to flow, $u'$ denotes velocity fluctuations in the longitudinal direction, $v'$ in the transverse direction, and $w'$ in the vertical direction. This calculation was done for each of the four heights we took measurements at in the flume, and for each Reynolds number and collector density in our parameter space. Because the velocimeter recorded three measurements simultaneously at each timepoint, TKE was calculated separately for these three measurements.

Turbulence calculated only from the bottom-most velocity measurements taken by the ADV was multiplied by a proportionality constant $C_{1}$ (0.19) and the density of water $\rho$ in order to estimate bed shear stress ($\tau_{0}$).
\[\tau_{0} = C_{1}[\frac{1}{2}\rho(<u^{'2}> + <v^{'2}> + <w^{'2}>)]\]
Reynolds stress and a modified TKE, in which only fluctuations in the vertical direction with respect to flow are taken into account, can also be used to estimate bed shear stress; these three methods of generating bed shear stress profiles are described in Biron et al. (2004), and the method that produced the smoothest profiles, in our case bed shear stress estimated using TKE, was ultimately chosen.
